Supplementary Materials

### 2022-12-07 manuscript/supplementary.tex
table

>>>>

\begin{table}
\centering
\begin{tabular}{lrrr}
  \hline
chrom &  accessible &  neutral &  both \\
  \hline
 chr1 &        42.4 &     64.4 &  22.9 \\
 chr2 &        46.8 &     58.7 &  23.7 \\
 chr3 &        44.1 &     62.9 &  24.8 \\
 chr4 &        44.0 &     59.3 &  21.5 \\
 chr5 &        44.1 &     58.0 &  21.4 \\
 chr6 &        45.0 &     58.0 &  22.1 \\
 chr7 &        44.4 &     65.8 &  26.4 \\
 chr8 &        43.8 &     61.2 &  23.1 \\
 chr9 &        39.2 &     64.5 &  20.3 \\
chr10 &        44.6 &     62.8 &  25.3 \\
chr11 &        42.7 &     63.5 &  23.4 \\
chr12 &        41.7 &     62.7 &  22.7 \\
chr13 &        39.7 &     62.0 &  18.3 \\
chr14 &        37.6 &     65.4 &  19.0 \\
chr15 &        37.0 &     69.4 &  20.3 \\
chr16 &        39.4 &     63.8 &  20.9 \\
chr17 &        40.4 &     64.0 &  22.3 \\
chr18 &        40.9 &     59.8 &  19.8 \\
chr19 &        30.9 &     69.8 &  18.0 \\
chr20 &        36.9 &     61.6 &  19.8 \\
chr21 &        31.6 &     68.6 &  18.2 \\
chr22 &        26.9 &     75.0 &  16.4 \\
\end{tabular}
\end{table}
